Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-30 Manuscript/manuscript.tex
Big update of data: added several new figures, improved all main-text figures, finished transition to SPCE.

The residence time histograms of \ce{Ca^{2+}}
in POPC bilayer are shown in Fig.~S\ref{fig:hist_residence_times} in SI 
from the ECC-lipid simulation with CaCl$_2$ concentration of 1~M
and from the CHARMM36 simulation with 450~mM concentration of
ECC-ions taken from the previous study \cite{javanainen17}
(the simulation data was downloaded from Ref.~\citenum{zenodo.259376}).
\todo{JOE: Plot a histogram of residence times based on our simulations and simulation from \citenum{javanainen17} and put it into SI.
}
\todo{It might be also better to do the analysis from ECC-lipid simulation with concentration closer
to the data in literature, i.e. 450mM.}
%Based on Fig. S17 in that work, Ref.~\citenum{javanainen17},
%we took the simulation with the apparent highest fluctuations of the number of bound calcium,
%which can be obtained at \url{https://doi.org/10.5281/zenodo.259376}
%and anaylsed the residence times.
% simulation: (Matti C36 with CaClMK, 800ns total):
Approximately 20\% of the \ce{Ca^{2+}} residence times in the CHARMM36 simulation are longer than
the lenght of the trajectory ($800\,\mathrm{ns}$),
and only less than 60\% of the bound residence times are shorter than the half
of the simulation length~(400~ns).
Even longer residence times are observed
in the other simulations with CHARMM36 and Slipids models reported in the previous work~\cite{javanainen17}.
At least order of magnitude faster exchange is observed in the
ECC-lipid model, where 90\% of the \ce{Ca^{2+}} residence times to a POPC membrane are 
shorter than $60\,\mathrm{ns}$, % exactly $53\,\mathrm{ns}$
and the longest observed residence time in the ECC-lipid simulation is $120\,\mathrm{ns}$, 
which is well below the total length of the simulation (200~ns).
The exchange of \ce{Na+} ions to a POPC membrane is
an order of magnitude faster, giving 90\%
of the residence times smaller than~$2\,\mathrm{ns}$,
the longest residence time being~$13\,\mathrm{ns}$. 
All the results are in line with the experimental estimation that 
the residence time of \ce{Ca^{2+}} at the individual PC headgroup 
is shorter than $10\,\mu\mathrm{s}$~\cite{altenbach84}.

>>>>

The residence time histograms of \ce{Ca^{2+}}
in POPC bilayer are shown in Fig.~S\ref{fig:hist_residence_times} in SI 
from the ECC-lipid simulation with CaCl$_2$ concentration of 1~M
and from the CHARMM36 simulation with 450~mM concentration of
ECC-ions taken from the previous study \cite{javanainen17}
(the simulation data was downloaded from Ref.~\citenum{zenodo.259376}).
\todo{JOE: Plot a histogram of residence times based on our simulations and simulation from \citenum{javanainen17} and put it into SI.
}
\todo{It might be also better to do the analysis from ECC-lipid simulation with concentration closer
to the data in literature, i.e. 450mM.}
%Based on Fig. S17 in that work, Ref.~\citenum{javanainen17},
%we took the simulation with the apparent highest fluctuations of the number of bound calcium,
%which can be obtained at \url{https://doi.org/10.5281/zenodo.259376}
%and anaylsed the residence times.
% simulation: (Matti C36 with CaClMK, 800ns total):
Approximately 20\% of the \ce{Ca^{2+}} residence times in the CHARMM36 simulation are longer than
the lenght of the trajectory ($800\,\mathrm{ns}$),
and only less than 60\% of the bound residence times are shorter than the half
of the simulation length~(400~ns).
Even longer residence times are observed
in the other simulations with CHARMM36 and Slipids models reported in the previous work~\cite{javanainen17}.
At least order of magnitude faster exchange is observed in the
ECC-lipid model, where 90\% of the \ce{Ca^{2+}} residence times to a POPC membrane are 
shorter than $60\,\mathrm{ns}$, % exactly $53\,\mathrm{ns}$
and the longest observed residence time in the ECC-lipid simulation is $141\,\mathrm{ns}$, 
which is well below the total length of the simulation (200~ns).
The exchange of \ce{Na+} ions to a POPC membrane is
an order of magnitude faster, giving 90\%
of the residence times smaller than~$1\,\mathrm{ns}$,
the longest residence time being~$6\,\mathrm{ns}$. 
All the results are in line with the experimental estimation that 
the residence time of \ce{Ca^{2+}} at the individual PC headgroup 
is shorter than $10\,\mu\mathrm{s}$~\cite{altenbach84}.
